NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2019-02-05 Manuscript/manuscriptPS.tex

%\label{}
\section{Introduction}
Phosphatidylserine (PS) is the most common negatively
charged lipid in eykaryotic membranes.
PS lipids compose 8.5\% of total lipid weight of erythrocytes,
but the abundance varies between different organelles up to
25-35\% in plasma membrane \cite{lemmon08,leventis10,li14}.
Despite of the relatively low abundance, PS lipids
are important signaling molecules. They interact with
signaling proteins \cite{leventis10}, regulate
surface charge and protein localization \cite{yeung08}, and
induce protein aggregation \cite{zhao04,gorbenko06}.
Some protein domains spesifically interact PS lipids,
while others are attracted by general electrostatics and the
binding can be regulated by calcium \cite{leventis10}.
Therefore, the structural details
of lipid headgroups and the details of cation binding
are crucial for the PS mediated signaling processes.

>>>>

%\label{}
\section{Introduction}
Phosphatidylserine (PS) is the most common negatively
charged lipid in eykaryotic membranes.
PS lipids compose 8.5\% of total lipid weight of erythrocytes,
but the abundance varies between different organelles up to
25-35\% in the cytosolic leaflet of plasma membranes \cite{lemmon08,leventis10,li14}.
Despite of the relatively low abundance, PS lipids
are important signaling molecules. They interact with
signaling proteins \cite{leventis10}, regulate
surface charge and protein localization \cite{yeung08}, and
induce protein aggregation \cite{zhao04,gorbenko06}.
Some protein domains spesifically interact PS lipids,
while others are attracted by general electrostatics and the
binding can be regulated by calcium \cite{leventis10}.
Therefore, the structural details
of lipid headgroups and the details of cation binding
are crucial for the PS mediated signaling processes.
